\chapter{I Ain't Afraid of Dark Lords}

This was the original version of Chapter 9. It was replaced because—while
many readers did enjoy it—many other readers had \emph{massive} allergies to
songs in fanfics, for reasons that should not much need belaboring. I didn't
want to drive readers away before they got to Ch. 10.

Lee Jordan is the fellow prankster of Fred and George (in canon). "Lee Jordan"
had sounded like a Muggleborn name to me, implying that he would be capable of
instructing Fred and George on a tune that Harry would know. This was not as
obvious to some readers as it was to your author.
\sbreak
Draco went to Slytherin, and Harry breathed a small sigh of relief. It had
\emph{seemed} like a sure thing, but you never did know what tiny event might
upset the course of your master plan.

They were approaching the Ps now{\el}

And over at the Gryffindor table, there was a whispered conversation.

"\emph{What if he doesn't like it?}"

"\emph{He's got no right to not like it}—"

"\emph{—not after the prank he played on}—"

"\emph{—Neville Longbottom, his name was}—"

"\emph{—he's as fair a fair target now as fair can be.}"

"\emph{All right. Just make sure you don't forget your parts.}"

"\emph{We've rehearsed it often enough}—"

"\emph{—over the last three hours.}"

And Minerva McGonagall, from where she stood at the speaker's podium of the
Head Table, looked down at the next name on her list. \emph{Please don't let
him be a Gryffindor please don't let him be a Gryffindor OH PLEASE don't let
him be a Gryffindor{\el}} She took a deep breath, and called:

"Potter, Harry!"

There was a sudden silence in the hall as all whispered conversation stopped.

A silence broken by a horrible buzzing noise that modulated and changed in
hideous mockery of musical melody.

Minerva's head jerked around, shocked, and identified the buzzing noise as
coming from the Gryffindor direction, where They were \emph{standing on top of
the table} blowing into some kind of tiny devices held against Their lips. Her
hand started to drop to her wand, to \emph{Silencio} the lot of Them, but
another sound stopped her.

Dumbledore was chuckling.

Minerva's eyes went back to Harry Potter, who had only just started to step out
of line before he'd stumbled and halted.

Then the young boy began to walk again, moving his legs in odd sweeping
motions, and waving his arms back and forth and snapping his fingers, in
synchrony with Their music.

\begin{center}
\emph{To the tune of ``Ghostbusters''}

\emph{(As performed on the kazoo by Fred and George Weasley,
and sung by Lee Jordan.)}

.

\emph{There's a Dark Lord near?\\
Got no need to fear\\
Who you gonna call?}
\end{center}

"\shout{Harry Potter}!" shouted Lee Jordan, and the Weasley twins performed a
triumphant chorus.

\begin{center}
\emph{With a Killing Curse?\\
Well it could be worse.\\
Who you gonna call?}
\end{center}

"\shout{Harry Potter}!" There were a lot more voices shouting it this time.

The Weasley Horrors went off into an extended wailing, now accompanied by some
of the older Muggleborns, who had produced their own tiny devices, Transfigured
out of the school silverware no doubt. As their music reached its anticlimax,
Harry Potter shouted:

\begin{center}
\emph{I ain't afraid of Dark Lords!}
\end{center}

There was cheering then, especially from the Gryffindor table, and more
students produced their own antimusical instruments. The hideous buzzings
redoubled in volume and built to another awful crescendo:

\begin{center}
\emph{I ain't afraid of Dark Lords!}
\end{center}

Minerva glanced to both sides of the Head Table, afraid to look but with all
too good a notion of what she would see.

Trelawney frantically fanning herself, Flitwick looking on with curiosity,
Hagrid clapping along to the music, Sprout looking severe, and Quirrell gazing
at the boy with sardonic amusement. Directly to her left, Dumbledore humming
along; and directly to her right, Snape gripping his empty wine goblet,
white-knuckled, so hard that the thick silver was slowly deforming.

\begin{center}
\emph{Dark robes and a mask?\\
Impossible task?\\
Who you gonna call?\\
\shout{Harry Potter}!}

\emph{Giant Fire-Ape?\\
Old bat in a cape?\\
Who you gonna call?\\
\shout{Harry Potter}!}
\end{center}

Minerva's lips set in a white line. She would have words with Them about that
last verse, if They thought she was powerless because it was the first day of
school and Gryffindor had no points to take away. If They didn't care about
detentions then she would find something else.

Then, with a sudden gasp of horror, she looked in Snape's direction,
\emph{surely} he realized the Potter boy must have no idea who that was talking
about—

Snape's face had gone beyond rage into a kind of pleasant indifference. A faint
smile played about his lips. He was looking in the direction of Harry Potter,
not the Gryffindor table, and his hands held the crumpled remains of a former
wine goblet{\el}

And Harry walked forwards, sweeping his arms and legs through the motions of
the Ghostbusters dance, keeping a smile on his face. It was a great setup, had
caught him completely by surprise. The least he could do was play along and not
ruin it all.

Everyone was cheering him. It made him feel all warm inside and sort of awful
at the same time.

They were cheering him for a job he'd done when he was one year old. A job he
hadn't really finished. Somewhere, somehow, the Dark Lord was still alive.
Would they have been cheering quite so hard, if they knew that?

But the Dark Lord's power \emph{had} been broken once.

And Harry would protect them again. If there was in fact a prophecy and that
was what it said. Well, actually regardless of what any darn prophecy said.

All those people believing in him and cheering him—Harry couldn't stand to
let that be false. To flash and fade like so many other child prodigies. To be
a disappointment. To fail to live up to his reputation as a symbol of the
Light, never mind \emph{how} he'd gotten it. He would absolutely, positively,
no matter how long it took and even if it killed him, fulfill their
expectations. And then go on to \emph{exceed} those expectations, so that
people wondered, looking back, that they had once asked so little of him.

And he shouted out the lie that he'd invented because it scanned well and the
song called for it:

\begin{center}
\emph{I ain't afraid of Dark Lords!\\
I ain't afraid of Dark Lords!}
\end{center}

Harry took his last steps toward the Sorting Hat as the music ended. He swept a
bow to the Order of Chaos at the Gryffindor table, and then turned and swept
another bow to the other side of the hall, and waited for the applause and
giggling to die away{\el}
