\chapter{Alternate Endings of "Self-Awareness"}
When chapter 9 was first posted, Eliezer said that if anyone guessed what the last
sentence was talking about before the next update, he would tell them the entire rest of the plot.

The offer spurred a \emph{lot} of interesting attempts. The first omake below is
taken directly from my personal favorite answer, by Meteoricshipyards. The
second is based on Kazuma's suggestion for what "has never happened before",
the third on a combination of yoyoente and dougal74, the fourth on wolf550e's
review of chapter 10. The one that starts with `K', and the one just above
that, are from DarkHeart81. The others are my own. Anyone who wants to pick up
one of my own ideas and run with them, particularly the last one, is welcome to
do so. And before I get 100 indignant complaints, yes, I am well aware that the
legislative body of the UK is the House of Commons in Parliament.
\sbreak
{\el}In the back of his mind, he wondered if the Sorting Hat was genuinely
\emph{conscious} in the sense of being aware of its own awareness, and if so,
whether it was satisfied with only getting to talk to eleven-year-olds once per
year. Its song had implied so: \emph{Oh, I'm the Sorting Hat and I'm okay, I
sleep all year and I work one day{\el}}

When there was once more silence in the room, Harry sat on the stool and
\emph{carefully} placed onto his head the 800-year-old telepathic artifact of
forgotten magic.

Thinking, just as hard as he could: \emph{Don't Sort me yet! I have questions I
need to ask you! Have I ever been Obliviated? Did you Sort the Dark Lord when
he was a child and can you tell me about his weaknesses? Can you tell me why I
got the brother wand to the Dark Lord's? Is the Dark Lord's ghost bound to my
scar and is that why I get so angry sometimes? Those are the most important
questions, but if you've got another moment can you tell me anything about how
to rediscover the lost magics that created you?}

And the Sorting Hat answered, "\emph{No. Yes. No. No. Yes and no, next time
don't ask double questions. No.}" and out loud, "RAVENCLAW!"
\sbreak
"\emph{Oh, dear. This has never happened before{\el}}"

\emph{What?}

"\emph{I'm allergic to your hair shampoo}—"

And then the Sorting Hat sneezed, with a mighty "A-CHOO!" that echoed around
the Great Hall.

"Well!" Dumbledore cried jovially. "It seems Harry Potter has been sorted into
the new House of Achoo! McGonagall, you can serve as the Head of House Achoo.
You'd better hurry up on making arrangements for Achoo's curriculum and
classes, tomorrow is the first day!"

"But, but, but," stammered McGonagall, her mind in nearly complete disarray,
"who will be Head of House Gryffindor?" It was all she could think of, she
\emph{had} to stop this somehow{\el}

Dumbledore put a finger to his cheek, looking thoughtful. "Snape."

Snape's screech of protest nearly drowned out McGonagall's, "Then who will be
Head of \emph{Slytherin?}"

"Hagrid."
\sbreak
\emph{Don't Sort me yet! I have questions I need to ask you! Have I ever been
Obliviated? Did you Sort the Dark Lord when he was a child and can you tell me
about his weaknesses? Can you tell me why I got the brother wand to the Dark
Lord's? Is the Dark Lord's ghost bound to my scar and is that why I get so
angry sometimes? Those are the most important questions, but if you've got
another moment can you tell me anything about how to rediscover the lost magics
that created you?}

There was a brief pause.

\emph{Hello? Do I need to repeat the questions?}

The Sorting Hat screamed, an awful high-pitched sound that echoed through the
Great Hall and caused most of the students to clap their hands over their ears.
With a desperate yowl, it leapt off Harry Potter's head and bounded across the
floor, pushing itself along with its brim, and made it halfway to the Head
Table before it exploded.
\sbreak
"SLYTHERIN!"

Seeing the look of horror on Harry Potter's face, Fred Weasley thought faster
than he ever had in his life. In a single motion he whipped out his wand,
whispered "\emph{Silencio!}" and then "\emph{Changemyvoiceio!}" and finally
"\emph{Ventriliquo!}"

"Just kidding!" said Fred Weasley. "GRYFFINDOR!"
\sbreak
"\emph{Oh, dear. This has never happened before{\el}}"

\emph{What?}

"\emph{Ordinarily I would refer such questions to the Headmaster, who could ask
me in turn, if he wished. But some of the information you've asked for is not
only beyond your own user level, but beyond the Headmaster's.}"

\emph{How can I raise my user level?}

"\emph{I'm afraid I am not allowed to answer that question at your current user
level.}"

\emph{What options} are \emph{available at my user level?}

After that it didn't take long—

"ROOT!"
\sbreak
"\emph{Oh, dear. This has never happened before{\el}}"

\emph{What?}

"\emph{I've had to tell students before that they were mothers—it would break
your heart to know what I saw in their minds—but this is the first time I've
ever had to tell someone they were a father.}"

\emph{WHAT?}

"\emph{Draco Malfoy is carrying your baby.}"

\emph{WHAAAAAAAT?}

"\emph{To repeat: Draco Malfoy is carrying your baby.}"

\emph{But we're only eleven—}

"\emph{Actually, Draco is secretly thirteen years old.}"

\emph{B-b-but men can't get pregnant—}

"\emph{And a girl under those clothes.}"

\emph{BUT WE'VE NEVER HAD SEX, YOU IDIOT!}

"\emph{SHE OBLIVIATED YOU AFTER THE RAPE, MORON!}"

Harry Potter fainted. His unconscious body fell off the stool with a dull thud.

"RAVENCLAW!" called out the Hat from where it lay on top of his head. That had
been even funnier than its first idea.
\sbreak
"ELF!"

Huh? Harry remembered Draco mentioning a `House Elf', but what was that exactly?

Judging by the appalled looks dawning on the faces around him, it wasn't
anything good—
\sbreak
"PANCAKES!"
\sbreak
"REPRESENTATIVES!"
\sbreak
"\emph{Oh, dear. This has never happened before{\el}}"

\emph{What?}

"\emph{I've never Sorted someone who was a reincarnation of Godric Gryffindor
AND Salazar Slytherin AND Naruto.}"
\sbreak
"ATREIDES!"
\sbreak
"Fooled you again! HUFFLEPUFF! SLYTHERIN! HUFFLEPUFF!"
\sbreak
"PICKLED STEWBERRIES!"
\sbreak
"KHAAANNNN!"
\sbreak
At the Head Table, Dumbledore went on smiling benignly; small metallic sounds
occasionally came from Snape's direction as he idly compacted the twisted
remains of what had once been a heavy silver wine goblet; and Minerva
McGonagall clenched the podium in a white-knuckled grip, knowing that Harry
Potter's contagious chaos had infected the Sorting Hat itself.

Scenario after scenario played out through Minerva's head, each worse than the
last. The Hat would say that Harry was too evenly balanced between Houses to
Sort, and decide that he belonged to all of them. The Hat would proclaim that
Harry's mind was too strange to be Sorted. The Hat would demand that Harry be
expelled from Hogwarts. The Hat had gone into a coma. The Hat would insist that
a whole new House of Doom be created just to accomodate Harry Potter, and
\emph{Dumbledore would make her do it{\el}}

Minerva remembered what Harry had told her in that disastrous trip to Diagon
Alley, about the{\el} planning fallacy, she thought it had been{\el} and
how people were usually too optimistic, even when they thought they were being
pessimistic. It was the sort of information that preyed on your mind, dwelling
in it and spinning off nightmares{\el}

But what was the \emph{worst} that could happen?

Well{\el} in the \emph{worst-case scenario,} the Hat would assign Harry to a
whole new House. Dumbledore would insist that she do it—create a whole new
House just for him—and she'd have to rearrange all the class schedules on the
first day of term. And Dumbledore would remove her as Head of House Gryffindor,
and give her beloved House over to{\el} Professor Binns, the History ghost;
and she would be assigned as Head of Harry's House of Doom; and she would
futilely try to give the child orders, deducting point after point without
effect, while disaster after disaster was blamed on her.

Was that the worst-case scenario?

Minerva honestly didn't see how it could be any worse than that.

And even in the very worst case—no matter \emph{what} happened with
Harry—it would all be over in seven years.

Minerva felt her knuckles slowly relax their white-knuckled grip on the podium.
Harry had been right, there was a kind of comfort in staring directly into the
furthest depths of the darkness, knowing that you had confronted your worst
fears and were now prepared.

The frightened silence was broken by a single word.

"Headmaster!" called the Sorting Hat.

At the Head Table, Dumbledore rose, his face puzzled. "Yes?" he addressed the
Hat. "What is it?"

"I wasn't talking to you," said the Hat. "I was Sorting Harry Potter into the
place in Hogwarts where he most belongs, namely the Headmaster's office—"
